# Data and server setup

Here we first create the test data that we will use later in combination with an
[h5serv](https://github.com/HDFGroup/h5serv) instance.

## Data preparation

We will use the two *sciex* test files from the `msdata` package.

```{r}
library(Spectra)
library(msdata)

fls <- dir(system.file("sciex", package = "msdata"), full.names = TRUE)

sps <- Spectra(fls, backend = MsBackendHdf5Peaks(),
               source = MsBackendMzR(), hdf5path = normalizePath("."))

```

## Server setup

To use the `h5serv` we install first the according docker image with `docker
pull hdfgroup/h5serv`. The server can then be started with `docker run -p
5000:5000 -d -v <mydata>:/data hdfgroup/h5serv` where `<mydata>` is the folder
path that contains any HDF5 files we want to serve. Use the browser to connect
to port 5000 to see if the server has started.


## Tests with the `hdf5client` package

Assuming we have started the above server we try to access files on it. Note
that there might be some problems if `R` is running within a docker too.

```{r}
library(rhdf5client)
s <- HSDSSource("http://host.docker.internal:5000", type = "h5serv")
f <- HSDSFile(s, "20171016_POOL_POS_1_105-134.hdfgroup.org")
f <- HSDSFile(s, "sciex")

s <- HSDSSource("http://localhost:5000", type = "h5serv")
f <- HSDSFile(s, "20171016_POOL_POS_1_105-134.h5")
d <- HSDSDataset(f, "/spectra")

HSDSArray("http://host.docker.internal:5000", "h5serv", "20171016_POOL_POS_1_105-134.hdfgroup.org",
          "spectra/1")

s <- H5S_source("http://host.docker.internal:5000", "hdfgroup.org")

```
